A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-12 4_method.tex
better MAT explanation and better segment generation figures

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/segment_generation.pdf}
\caption{
Generating toolpaths on a aprt of the test outline shape which is fully shown in \cref{shape_decomp_complex}.
Each edge is assigned toolpath junctions (yellow) which are connected together as shown in the singled out trapezoid.
By following the trapezoids along the domain (cyan) of a single outline polygon,
the segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
}
\label{segment_generation}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{sources/method/segment_generation.pdf}
\caption{
Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomp_complex}.
Each edge is assigned toolpath junctions (yellow) which are connected together as shown in the singled out trapezoid.
By following the trapezoids along the domain (cyan) of a single outline polygon,
the segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
}
\label{segment_generation}
\end{figure}
